%*******************************************************
% System Feasibility
%*******************************************************
\pdfbookmark[1]{System Feasibility}{System Feasibility}
\chapter{System Feasibility}

% Economic
\section{Economic}
\hspace*{4mm}The end goal of this hardware is to be able to be used by the general population, which means costs must be kept relatively low. We wish our users to be able to purchase the hardware for and set up their own FollowThrough system as we will not be selling or distributing the product. This economic feasibility report will include analysis of costs, benefits, and project timing.

\subsection{Costs}
The below lists all expected costs, direct and indirect, with an approximation of how much it will cost.\\
\\
Direct Costs:
\begin{itemize}
    \item Purchase of hardware pieces that the FollowThrough utilizes
    \begin{itemize}
        \item Arduino/Raspberry Pi (\$50)
        \item Distance sensor (\$15)
        \item Webcam (\$25)
    \end{itemize}
    \item Purchase of basketballs for testing (\$20)
    \item Renting gym space for testing (\$150)
    \item Web server costs (\$40)
\end{itemize}
Indirect costs:
\begin{itemize}
    \item Six months of development time from four student developers (No cost)
\end{itemize}
Total Costs: $\$300.00$

\newpage
\subsection{Benefits}
The benefits of this project are non-monetary since it will be open source. However, the project does provide non-monetary benefits to not only the creators, but anyone who uses the open source software.\\
\begin{itemize}
    \item Allowing players to further improve their basketball skills without incurring massive costs.
    \item Creating an open source version of the software in an attempts to lower costs.
    \item Completing the capstone course at McMaster University.
\end{itemize}

\subsection{Analysis}
Since the development costs for this project are so low there is very little downside to developing a product like this. The benefits of a developing this system far outweigh the minor monetary costs, therefore this analysis shows that the project should proceed.

% Technical Feasibility
\section{Technical Feasibility}
\subsection{Method of production}
\hspace*{4mm}Inputs have been listed above under costs. There is no limit in availability of hardware, however there is limited availability of gym time which could be a limiting factor in our ability to test. A potential problem with the development of the system will be whether features have to be cut to fit the development period into a six month time frame. Developing three separate subsystems will take a significant amount of time and unfortunately we cannot devote ourselves full time to this project.

\subsection{Production technique}
For the development of this project we will use synchronous development. The tasks of the project will be divided and the three subsystems will be developed at the same time by different developers. This will allow optimal use of developer time and allow us to demonstrate functionality of all subsystems as development occurs.

\subsection{Project requirements}
\hspace*{4mm}All project requirements are listed above. 

\subsection{Project Location}
\hspace*{4mm}This project does not have a specific location, the device should be able to be moved and be used on any basketball court. One limitation to this is outdoor use, in which favorable weather is necessary.

% Alternatives
\section{Alternatives}
\hspace*{4mm}Currently the main alternative to FollowThrough is the use of a Shooting Coach. This has been the established way to improve shooting percentages from the beginning of basketball. However, in recent years there have been a few ventures into comprehensive systems to track shooting statistics. The current system that we hope FollowThrough will be able to compare to is “Noah”. The Noah system provides similar stat tracking functionality (arc, depth, left/right) and allows a player to track their analytics via the web. However, Noah comes at a large cost of nearly $\$4000.00$ for use on only  one half of a basketball court, a full court system costs nearly $\$5000.00$. At this price point only large institutions would be able to provide their players with this service. FollowThrough hopes to provide the ability for any player to purchase the components and setup the system by themselves. 