% Functional Requirements
%*******************************************************
\pdfbookmark[1]{Functional Requirements}{Functional Requirements}
\chapter{Functional Requirements}

\section{Inputs Requirement}
\hspace*{4mm} The inputs will include the user taking the shot the laptop is setup to measure, as well as prior registration on our website from the user if they wish to track their progress overtime. 

\section{Outputs Requirement}
\hspace*{4mm} The output will include a detailed description of the user's shot arch presented to them in an easily readable format. A comparison will be shown between the user's shot arc and the ideal one for basketball. It will also include their shot success rate presented to them via the web interface. Also on the web application there will be statistics and other data that will showcase the user's progress over a long period of time. 

\section{Interfaces Requirement}
\hspace*{4mm} The program will have two user interfaces. The first one will be available offline and will be a live view of the users shot and a login portal. Everytime the user takes a shot,the local program will give feedback both on screen and will also give an auditory signal. The second interface will be the web application once they log into their account online. This will present the same kind of information but will also showcase the user's entire history with the program, not only recent shot data. 

\section{Algorithm Complexity Requirement}
\hspace*{4mm} The algorithm used in OpenCV to track the ball will be simple enough to run on any modern laptop without trouble or intensive CPU usage. It will not use proprietary software or drivers that would only run on select devices. 

\newpage
\section{Fault Tolerance Requirement}
\hspace*{4mm} The application will be accurate enough to give the user meaningful feedback about how close their shot arc is to the ideal basketball shot arc. It will at the very least indicate to the user if their shot arc is too high or low. This application is designed to be usable by anyone with a modern laptop camera, not only those with high end cameras. As a result there will likely be some slight inaccuracies with the ball tracking but nothing that will prevent this application from providing useful information. 