%*******************************************************
% Project Drivers
%*******************************************************
\pdfbookmark[1]{Customer's Needs}{Customer's Needs}
\chapter{Customer's Needs}

% Needs of the Customers
\section{Needs of the Customers}
\begin{itemize}
    \item Eliminate the need of other people being on the court to provide feedback.
    \item Provide real time advice to growing basketball players.
    \item To improve basketball shot form and shot technique.
    \item Works with many camera's and laptop's.
    \item Save data to be reviewed at a later date.
\end{itemize}

% Who are the customers?
\section{Who are the Customers?}

\subsection{The Customers}
\begin{itemize}
    \item Basketball players of any skill level.
    \item Coaches, teams and schools
    \item Programmers interested in a practical application of image recognition.
\end{itemize}

\subsection{Priorities Assigned to Users}
\begin{itemize}
    \item \textbf{Primary Users:} Regular basketball players.
    \item \textbf{Secondary Users:} Basketball coaches.
    \item \textbf{ Tertiary Users:} Developers, testers and project supervisors.
\end{itemize}

\subsection{User Participation}
\begin{itemize}
    \item Users must set up the hardware in the appropriate locations.
    \item Users must create their own accounts where the information will be saved.
\end{itemize}
 
\subsection{Maintenance Users}
\begin{itemize}
    \item The Developers of the project.
    \item The Testers of the project.
\end{itemize}



