%*******************************************************
% Non-Functional Requirements
%*******************************************************
\pdfbookmark[1]{Non-Functional Requirements}{Non-Functional Requirements}
\chapter{Non-Functional Requirements}

% Look and Feel Requirements
\section{Look and Feel Requirements}
\subsection{Appearance Requirements}
\hspace*{4mm}The graphical interface designed to provide the user with feedback will be very simple to understand. It will be designed to display properly on all modern web browsers. 


\subsection{Style Requirements}
\hspace*{4mm}Stylistically the software and hardware will not be obtrusive to the user in any sense.

% Usability and Humanity Requirements
\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
\hspace*{4mm} A guide will be provided that will instruct the user on how to set up the application. For the web application where the data will be sent, the interface will be intuitive so that the user will be visually guided to relevant information.

\subsection{Personalization and Internationalization Requirements}
\hspace*{4mm}FollowThrough will have very few elements in which translation is needed. Basketball statistics are referenced in similar manners all over the world, mostly in English.
 
\subsection{Learning Requirements}
\hspace*{4mm}The only part that requires learning in the case of this product would be setting up the hardware in appropriate positions. That will be accommodated for by giving the user a guide. The rest of the program is fairly straight forward and requires nothing more than common sense.
 
\subsection{Understandability and Politeness Requirements}
\hspace*{4mm}This product will use terminology that is friendly for any user and on top of that will also hide any unnecessary processes from the user to avoid confusion.
 
\subsection{Accessibility Requirements}
\hspace*{4mm}The product will give both auditory and visual instruction throughout its features to ensure accessibility.
 
% Performance Requirements
\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
\hspace*{4mm}FollowThrough will provide feedback in real time to the user. This means that within a few seconds of recognizing the ball has been shot the user should hear or see some feedback.
 
\subsection{Safety-Critical Requirements}
\hspace*{4mm}This product was not built to work during inclement weather. It must be protected from the rain or not used outside.
 
\subsection{Precision or Accuracy Requirements}
\hspace*{4mm}This product will return to the user information that is accurate with only a small degree of error so that the player does not find FollowThrough detrimental to their form.
 
\subsection{Reliability and Availability Requirements}
\hspace*{4mm}This product is designed to be used on a Basketball court and will be available to anyone who wishes to purchase the equipment and set up the devices..

\subsection{Robustness Requirements}
\hspace*{4mm}In the case of battery failure or any sort of power related disruption the product is to save any data that it can.

If any component of the product becomes disconnected the software will inform the user so that they may remedy the problem.
 
\subsection{Capacity Requirements}
\hspace*{4mm}As of right now the capacity of the product is only a single person. This may change in a later revision.
 
\subsection{Scalability or Extensibility Requirements}
\hspace*{4mm}FollowThrough is to be able to scale from one device to another and work cross-platform.
 
\subsection{Longevity Requirements}
\hspace*{4mm}This product is designed to last as long as any average computer.

% Operational and Environmental Requirements
\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\hspace*{4mm}The expected physical environment for this product would be on the Basketball court.
 
\subsection{Requirements for Interfacing with Adjacent Systems}
\hspace*{4mm}As mentioned previously this product is to work with various operating systems on various devices.
 
\subsection{Productization Requirements}
\hspace*{4mm}This product will require installation both physically and on the Basketball court.
 
\subsection{Release Requirements}
\hspace*{4mm}This product must be complete by April 2017 for its final demonstration.

% System and Need requirements
\section{System features to fulfill needs Requirement}
\hspace*{4mm} The system will feature an algorithm that will track the user's shot arc and compare it to the ideal shot arc in basketball. This will fulfill then user's need to measure their shot's accuracy and form. It will then provide the user feedback on their laptop as well as optionally online on how exactly to improve their shot. This will fulfill the user's need of shot improvement. 
 
% Subsystem requirements
\section{Subsystem Requirement}
\hspace*{4mm} The system will be split into 3 parts. 

\subsection{Laptop Requirements}
\hspace*{4mm}There will be the laptop which will run the necessary software and track the ball's position and arc in the air with its camera. 

\subsection{Basket Device Requirements}
\hspace*{4mm} There will be a device on the basket itself that will track shot success rate and the players position on the floor and send that information back to the laptop.

\subsection{Web Server Requirements}
\hspace*{4mm}There will be the web server which will record the user's data over time from the laptop which the user can access later via web interface to track progress. 

