%*******************************************************
% Step 4: On the Court, Hardware
%*******************************************************
\pdfbookmark[1]{Step 4: On the Court, Hardware}{Step 4: On the Court, Hardware}
\chapter{Step 4: On the Court, Hardware}

\setlength{\parindent}{0cm}

\section{Getting Down to Business}
In order to successfully complete this step you must have completed step three first. If you have not done that, go back to step three to continue.

\subsection{The Camera}
When you arrive on the court, the first step is to set up the camera in the correct way. To do so follow these steps:

\begin{enumerate}[{1)}]
\item The first step is to ensure you have a secure Internet connection. This will allow the application to communicate to the cloud server and the Raspberry Pi. Without this you will not be able to review your data at a later date.
\item The next step is to find a solid, safe and flat surface where you can put the recording device. You want to angle the device so that it can at least the entire half of the court you are playing on. You also want to make sure it is aligned in parallel with the court.
\item Once the device has been placed properly, you have to launch the FollowThrough application. The next section will detail how to connect the Pi to the application.
\end{enumerate}

\subsection{The Pi}
Before setting up the Pi you should set up the camera properly. If you have not done so refer to the previous section. To set up the Raspberry Pi follow these steps:

\begin{enumerate}[{1)}]
\item Hook the sensor to the rim on the Basketball net and have the sensor face inwards.
\item Power the device on.
\item Ensure it is connected to the Internet.
\item Return to your computer and pair the devices.
\end{enumerate}
