%*******************************************************
% Step 5: On the Court, Software (under construction)
%*******************************************************
\pdfbookmark[1]{Step 5: On the Court, Software (under construction)}{Step 5: On the Court, Software (under construction)}
\chapter{Step 5: On the Court, Software (under construction)}

\setlength{\parindent}{0cm}

\section{Using the Application}
In order to successfully use the application you must have completed all the previous steps. If you have not done so, return to those steps and complete them before trying to use the product. The use of the product is quite simple and is outlined below:

\begin{enumerate}[{1)}]
\item When you open the application it will prompt you for log-in information (to be implemented). Enter the same information you used for step two (or the information you created in step one).
\item Once the two devices are paired and you have properly set up the viewing angle, you can get started.
\item Press the start recording button in the user interface (still being made) to begin recording.
\item Play on the court for as long as you wish. You will receive live feedback as you do.
\item When you are done your session return to your device and press the stop recording button (to be implemented) to wrap up the recording process. The application will automatically send your data to the cloud so that you may access it at a later time
\end{enumerate}

If you wish to access your data later on, simply refer to step two for the process involved.\\ \\\textbf{For any additional questions you may e-mail the support staff directly at petrod@mcmaster.ca}